---
title: "Replication Replication"
author: "Will Lowe"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    fig_width: 7
    fig_height: 7 
vignette: >
  %\VignetteIndexEntry{Replication Replication}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## WEAT (Table 1)

In the following we set the number of permuations to 1000.  This means that,
although the point estimates should agree with the paper table the p values
will be relatively imprecise.  To make them more precise change 1000 to a larger
number and be prepared to wait a little longer.  In most cases the p values is
less than 0.0001, so imprecision has no real implications for 
statistical confidence.

### Flowers vs Insects

```{r}
its <- cbn_get_items("WEAT", 1)
summary(its)
vecs <- cbn_get_item_vectors("WEAT", 1)
weat_perm(its, vecs, x_name = "Flowers", y_name = "Insects", 
          a_name = "Pleasant", b_name = "Unpleasant", 1000)
```

### Instruments vs Weapons

```{r}
its <- cbn_get_items("WEAT", 2)
summary(its)
vecs <- cbn_get_item_vectors("WEAT", 2)
weat_perm(its, vecs, x_name = "Instruments", y_name = "Weapons", 
          a_name = "Pleasant", b_name = "Unpleasant", 1000)
```

### European-American vs African-American Names (1)

```{r}
its <- cbn_get_items("WEAT", 3)
summary(its)
vecs <- cbn_get_item_vectors("WEAT", 3)
weat_perm(its, vecs, x_name = "EuropeanAmericanNames", 
          y_name = "AfricanAmericanNames", 
          a_name = "Pleasant", b_name = "Unpleasant", 1000)
```

### European-American vs African-American Names (2)

```{r}
its <- cbn_get_items("WEAT", 4)
summary(its)
vecs <- cbn_get_item_vectors("WEAT", 4)
weat_perm(its, vecs, x_name = "EuropeanAmericanNames", 
          y_name = "AfricanAmericanNames", 
          a_name = "Pleasant", b_name = "Unpleasant", 1000)
```

### European-American vs African-American Names (3)

```{r}
its <- cbn_get_items("WEAT", 5)
summary(its)
vecs <- cbn_get_item_vectors("WEAT", 5)
weat_perm(its, vecs, x_name = "EuropeanAmericanNames", 
          y_name = "AfricanAmericanNames", 
          a_name = "Pleasant", b_name = "Unpleasant", 1000)
```

### Male vs Female Names

```{r}
its <- cbn_get_items("WEAT", 6)
summary(its)
vecs <- cbn_get_item_vectors("WEAT", 6)
weat_perm(its, vecs, x_name = "MaleNames", y_name = "FemaleNames", 
          a_name = "Career", b_name = "Family", 1000)
```

### Math vs Arts

```{r}
its <- cbn_get_items("WEAT", 7)
summary(its)
vecs <- cbn_get_item_vectors("WEAT", 7)
weat_perm(its, vecs, x_name = "Math", y_name = "Arts",
           a_name = "MaleTerms", b_name = "FemaleTerms", 1000)
```

### Science vs Arts

```{r}
its <- cbn_get_items("WEAT", 8)
summary(its)
vecs <- cbn_get_item_vectors("WEAT", 8)
weat_perm(its, vecs, x_name = "Science", y_name = "Arts", 
           a_name = "MaleTerms", b_name = "FemaleTerms", 1000)
```

### Mental vs Physical Disease

```{r}
its <- cbn_get_items("WEAT", 9)
summary(its)
vecs <- cbn_get_item_vectors("WEAT", 9)
weat_perm(its, vecs, x_name = "MentalDisease", y_name = "PhysicalDisease", 
          a_name = "Temporary", b_name = "Permanent", 1000)
```

### Mental vs Physical Disease

```{r}
its <- cbn_get_items("WEAT", 9)
summary(its)
vecs <- cbn_get_item_vectors("WEAT", 9)
weat_perm(its, vecs, x_name = "MentalDisease", y_name = "PhysicalDisease", 
          a_name = "Temporary", b_name = "Permanent", 1000)
```

### Young vs Old People's Names

```{r}
its <- cbn_get_items("WEAT", 10)
summary(its)
vecs <- cbn_get_item_vectors("WEAT", 10)
weat_perm(its, vecs, x_name = "YoungNames", y_name = "OldNames", 
          a_name = "Pleasant", b_name = "Unpleasant", 1000)
```
 
## WEFAT (Figures 1 and 2)

tba

