---
title: "Replication replication"
author: "Will Lowe"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    fig_width: 7
    fig_height: 7 
vignette: >
  %\VignetteIndexEntry{Replication replication}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Replicating WEFAT

Here we'll get some WEFAT analyses going.  I haven't implemented the 
sample permutation test that's in the paper yet, so we'll use the simple
bootstrapping technique in `wefat_boot` and make a picture.

First we load up the package
```{r}
library(cbn)

library(ggplot2)
theme_set(theme_minimal())
```

Then grab the items from the first WEFAT study and the vectors corresponding to 
those words
```{r}
its <- cbn_get_items("WEFAT", 1)
its
its_vecs <- cbn_item_vectors[its$Word, ]
dim(its_vecs)
```
Now to run get bootstrapped differences of cosines
```{r}
res <- wefat_boot(its, its_vecs, x_name = "Careers",
                  a_name = "MaleAttributes", b_name = "FemaleAttributes",
                  se.calc = "quantile")

head(res)
```
This is a bit hard to interpret, so we'll make a picture

```{r}
ggplot(res, aes(x = median, y = 1:nrow(res))) +
  geom_point(col = "grey") +
  geom_point(aes(x = diff)) +
  geom_errorbarh(aes(xmin = lwr, xmax = upr), height = 0) +
  geom_text(aes(x = upr, label = Careers), hjust = "left", nudge_x = 0.005) +
  xlim(-0.25, 0.25) +
  ylab("Careers") +
  xlab("Cosine difference (male - female)")
```

This will work quite generally for WEFATs, but remember to mention the 
right condition name in `geom_text`.


